Interfering with Noninterference \iftext\thanks{\bcp{Identify applicable funding agencies here (DARPA and NSF and...?)}}\fi

### 2020-01-07 main.tex
Nit
Test
Thoughts

Conventions:
%
\begin{itemize}
\item Words / addresses: $\word,\addr \in \WORDS$
\item Registers: $\reg \in \REGS$
\item Machine states:
$\mach \in \MACHS = (\WORDS\rightarrow\WORDS,\, \REGS\rightarrow\WORDS,\,
\WORDS)$
\item Abbreviations:
\\ $\mach(\addr) = \mach.1(\addr)$
\\ $\mach(\reg) = \mach.2(\reg)$
\\ $\mach(\textsc{pc}) = \mach.3$
\end{itemize}

@@

\iftext
\begin{itemize}
\item \bcp{Should we be talking about end-to-end or single-step NI?  I guess we
  have to begin with EENI and then get to SSNI as a (stronger) refinement.}

@@

\section{Tainting is noninterference($-$)}

\begin{itemize}
\item First intuition: A program is taint-NI if every pair of runs that don’t
branch on high data are noninterfering in the standard sense.  (i.e., they
don't write secret data to public locations and vice versa)
\item Better alternative: … for every pair of runs that take the same control path (even if they branch on tainted data)...
\item \bcp{We could even go a step farther: {\em truncate} the runs at the
  first point where their PCs differ, then demand NI.  This is a less
  demanding property and probably a less desirable one, as it doesn't
  predict the behavior of actual taint policies.  Discuss.}
\item (Are there any other variations of tainting that we could present in
this framework?)
\end{itemize}

\section{Separation is noninterference($+$)}

@@

\section{Stack protection is noninterference($++$)}

>>>>

Conventions:
%
\begin{itemize}
\item Words / addresses: $\word,\addr \in \WORDS$
\item Registers: $\reg \in \REGS$
\item Machine states: \bcp{Simplify: define {\em machine components} and
  then a machine state is a function from these to words.}
$\mach \in \MACHS = (\WORDS\rightarrow\WORDS,\, \REGS\rightarrow\WORDS,\,
\WORDS)$
\item Abbreviations:
\\ $\mach(\addr) = \mach.1(\addr)$
\\ $\mach(\reg) = \mach.2(\reg)$
\\ $\mach(\textsc{pc}) = \mach.3$
\end{itemize}

@@

\iftext
\begin{itemize}
\item Should we have an intermediate classification level (``internal'' or
something) and make the policy say that it's only bad for data to flow from
$\HIGH$ to $\LOW$?  This would correspond to more realistic taint policies.

\item \bcp{Should we be talking about end-to-end or single-step NI?  I guess we
  have to begin with EENI and then get to SSNI as a (stronger) refinement.}

@@

\section{Tainting is noninterference$-$}

\bcp{I'm having some trouble here.  Two main problems so far:
  \begin{itemize}
  \item Since the ``high part'' of the world keeps getting extended as
  tainted data gets written here and there, the only way for something
  ``bad'' to happen is for high/tainted data to get written to someplace
  that was designated as an ``output''.  We don't currently have any way of
  making such a designation.
  \item Even after adding a separate IFC-like label for ``internal'' cells
  (that are not scrambled but also not outputs), I'm not seeing clearly how
  to formulate taint checking as an NI-like property.  Need to think about
  it some more.
  \end{itemize}
}

\begin{itemize}
\item First intuition: A program is taint-NI if every pair of runs that don’t
branch on high data are noninterfering in the standard sense.  (i.e., they
don't write secret data to public locations and vice versa)
\item Better alternative: … for every pair of runs that take the same control path (even if they branch on tainted data)...
\item We could even go a step farther: {\em truncate} the runs at the
  first point where their PCs differ, then demand NI.  This is a less
  demanding property and probably a less desirable one, as it doesn't
  predict the behavior of actual taint policies.  Discuss.
\item Note that this is a super-simple property that doesn't really track
taint at all.  
\item (Are there any other variations of tainting that we could present in
this framework?)
\end{itemize}

\section{Separation is noninterference$+$}

@@

\section{Stack protection is noninterference$++$}
